### 2024-06-10 paper.tex
minor

\subsection*{Acknowledgements}
SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grants 771376 (to AMV) and 101071786 (to AMV and SA), from the DFG via SFB 873, and from the DKFZ.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.

>>>>

\subsection*{Acknowledgements}
SA and LPMK acknowledge funding by the Klaus Tschira Foundation (project 00.022.2019).
LPMK, MMB, LK, SC, and AMV acknowledge funding from the European Commission via ERC grants 771376 (to AMV) and 101071786 (to AMV and SA), from the DFG via SFB 873 (to AMV), and from the DKFZ.
We thank Alexey Uvarovskii for code refactoring and helpful suggestions on the source code.
